# Missing values

```{r include=FALSE}
#Load necessary libraries
require(jsonlite)
require(tibble)
require(dplyr)
require(ggplot2)
require(GGally)
```

Upon checking the number of missing values in each column in the parsed data frame, we found that most missing values occur to either irrelevant attributes of the tweets (such as coordinate data) or those information about retweets and the corresponding users (such as `ReTweetUserScreenName`).

```{r}
df <- as_tibble(read_json("./Data/allwords.json", simplifyVector = TRUE))
colSums(is.na(df))
```

The only attribute with missing values of concern is `TweetUserFollowRatio`, which is the ratio of the followers count to the following count of a Twitter user. After exploring the data, we discovered that the entries with missing `TweetUserFollowRatio` match exactly with those with 0 followers count and non-verified status. Since it makes sense that an user with no follower is not verified, it is safe to conclude that the 0 values in `TweetUserNumFollowers` are the direct cause of the missing values. Therefore, we simply substitute the missing values of `TweetUserFollowRatio` with 0.

```{r}
no_follower <- df %>% 
  filter(TweetUserNumFollowers == 0)

missing_col <- df[is.na(df$TweetUserFollowRatio),] %>%
  select(TweetUserDaysOn, TweetUserNumFavorites, TweetUserNumFollowers, TweetUserNumFollowing, TweetUserNumTweets, TweetUserVerified) %>% 
  mutate(TweetUserVerified = ifelse(TweetUserVerified, 1, 0))
  # mutate(ratio_missing = ifelse(is.na(TweetUserFollowRatio), "Yes", "No"))

ggparcoord(missing_col, columns = 1:6, order = c(1,2,5,4,3,6),
           # groupColumn = "ratio_missing", 
           alphaLines = 0.5, scale = "uniminmax",
           title = "Missing values in TweetUserFollowRatio with respect to other user-related variables") +
  coord_flip()
  
df <- df %>%
  filter(is.na(TweetUserFollowRatio)) %>%
  mutate(TweetUserFollowRatio = 0)
```

Looking into the distribution of user with no follower over each category, we found no clear relationship of whether having no follower indicates "quality" of an user.

```{r}
no_follower <- no_follower %>% 
  # count(Category)
  group_by(Category) %>%
  summarise(count = n()) %>%
  arrange(count) %>%
  mutate(Category = factor(Category, levels = Category))
  
ggplot(no_follower, aes(Category, count)) +
  geom_bar(stat = "identity") +
  ggtitle("Number of users with no follower per category")
```
